---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(OCepi)
library(dplyr)
library(jarvis)
library(ggplot2)
```

# jarvis

![](https://img.shields.io/badge/lifecycle-experimental-brightgreen.svg)

## Installation

```r
pak::pak("ericmshearer/jarvis")
```

## Tables

`tbl()`

-   `scaled` controls whether or not percent is multiplied by 100.
-   `digits` sets rounding.
-   For tables >1 variable, can pivot long to wide by setting `pivot` to TRUE.

```{r tbl1}
linelist |>
  tbl(Gender)
```

```{r tbl2}
linelist |>
  tbl(Gender, Ethnicity, pivot = TRUE)
```

`tbl_totals()`

-   Default calculates column totals. For row, set `loc` to "row". Or can use "both".
-   Name of summed cell defaults to "Total". To change, update `name`.

```{r tbl_totals}
linelist |>
  tbl(Race) |>
  tbl_totals()
```

`tbl_percentage()`

-   Control rounding via `digits`.
-   Default calculates column percentages. For row, set `loc` to "row".

```{r tbl_percentage}
linelist |>
  tbl(Race, Ethnicity, pivot = TRUE) |>
  tbl_percentage()
```

## Data Visualization

`scale_percent()`

For unscaled percentages (i.e. not multiplied by 100), update `scale` to FALSE. 

```{r scale_percent, fig.width = 14, fig.asp = 0.8}
linelist |>
  count(Race) |>
  mutate(percent = add_percent(n)) |>
  ggplot(aes(x = Race, y = percent)) +
  geom_bar(stat = "identity") +
  scale_x_discrete(label = wrap_labels(delim = "or")) +
  scale_y_continuous(expand = c(0,0), label = scale_percent()) +
  theme_apollo()
```


## Date/Time

`excel_date()`

```{r excel_date}
excel_date(as.numeric(45576))
```
